Hydras \& Co.

### 2023-07-12 doc/chapter-natural-deduction.tex
work on chapter-natural-deduction

\subsection{sketch of proof}

@@

\begin{project}[**]
  The type \texttt{SysPrf} has sort \texttt{Prop}, which prevent us from
extracting the underlying proof tree and its fringe from an hypothesis 
of the form $X\sdash f$. 
It would be nice (\emph{e.g.} for a better understanding of the proof of the deduction theorem) to be able to compute the the proof-tree built
by the proof of the deduction lemma. 
\end{project}

>>>>

\subsection{Sketch of proof}

@@

\begin{project}[**]
  The type \texttt{SysPrf} has sort \texttt{Prop}, which prevent us from
extracting the underlying proof tree and its fringe from an hypothesis 
of the form $X\sdash f$. 
It would be nice (\emph{e.g.} for a better understanding of the proof of the deduction theorem) to be able to compute the  proof-tree built
by the proof of the deduction lemma. 
On a fresh branch of the project, please change the definition of
\texttt{SysPrf} and fix the errors this change could cause in the rest of the files. 
\end{project}
